Advances in Robust Positive Invariant Set Computation

### 2015-03-02 draft.tex
Initial draft.

\usepackage{graphics}
\usepackage{epsfig}
% \usepackage{mathptmx}
% \usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{lpic}

@@

\begin{document}
  \title{Advances in Robust Positive Invariant Sets Computation}

@@

\section{Introduction}
\begin{equation}\label{eq:system:equation}
	x^+ = \Psi x + v
\end{equation}
\begin{equation}\label{eq:definition:mrpi:set:state:dependent}
	\mathcal X^\infty = \{x:\Psi x + v\in\mathcal X^\infty\; \forall v\in\mathcal V(x)\}
\end{equation}
\begin{equation}\label{eq:PWA:distrubance:set}
	\mathcal V(x) = \left\{v: Gv\leq\max\{{\bf{1}},H^x x\}\right\}
\end{equation}
\section{Parametrically convex set operations}
In this section we discuss sets that depend on a state-like parameter (so called point-to-set maps, 
see~\cite{Hogan:1973}), and extend the existing set algebra~\cite{blanchini:2007} to 
accommodate such sets. We present the general case first, then derive the computation of
the case with piece-wise affine sets.

%First we introduce
    \begin{defn}[Parametric Convexity]\label{def:parametric:convexity}
      Let $X\subseteq\mathbb R^n$ and $Y\subseteq\mathbb R^m$ and $T:X\rightarrow Y$, $X\ni s\mapsto T(s)\subset Y$ be a 
      continuous point-to-set map. The map $T$ is called \emph{parametrically convex} if it satisfies
      \begin{equation}\label{eq:pconvexdef}
        T(\lambda s_1 + (1-\lambda)s_2)\subseteq\lambda T(s_1) \oplus (1-\lambda) T(s_2)
      \end{equation}
      for all $s_1,s_2\in X$ and $\lambda\in[0,1]$.
    \end{defn}

In (\ref{eq:pconvexdef}), $\oplus$ denotes the Minkowski set addition
      \begin{equation}
        \mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}.
      \end{equation}
%      see~\cite{blanchini:2007}.
%    Note also that Definition~\ref{def:parametric:convexity} does not require $X$ and $Y$ to be of equal dimensions.
    In the following we will need to be able to compute differences of sets
    analogous to the Pontryagin difference in~\cite{Kolmanovsky:1998} but using parametrised 
    sets, this is defined as follows:

    \begin{defn}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
Let $S\subseteq X$ and let $T:X\to X$ be a continuous point-to-set map,
%      Let $T$ be a continuous point-to-set map from $X$ to $X$, and let $S\subseteq X$, 
then the \emph{parametric Pontryagin difference} $S\ominus T(S)$ is 
      \begin{equation}
        S\ominus T(S) = \left\{x\in X: \{x\} \oplus T(x)\subseteq S\right\},
      \end{equation}
      where $T(S)$ denotes the image of $S$ under the map $T$.
    \end{defn}

@@

    \begin{thm}\label{thm:convexity:of:pontryagin:difference}
      Let $S\subseteq X$ be a convex set and let $T:X\rightarrow X$ be a parametrically convex point-to-set
      map, then $S\ominus T(S)$ is convex. 
    \end{thm}
    \begin{proof}
      Define $ Z =  S\ominus T( S)$ and let $z_1,z_2\in Z$, then
      by definition of the parametric Pontryagin difference, we have
      \begin{equation}
        \{z_i\} \oplus T(z_i) \subseteq S,\; i=1,2.
      \end{equation}
      To see that $ Z$ is convex we show that line segments between
      all possible $z_1$ and $z_2$ are subsets of $ Z$, i.e.~for all $\lambda \in [0,1]$,
%      \begin{equation}\label{eq:proof:of:parametric:convexity}
      \[\begin{aligned}
        \{ \lambda z_1 + (1-&\lambda)z_2
        \}\oplus T\left( \lambda z_1 + (1-\lambda)z_2\right)\\
        \subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
        \right\}\oplus \lambda T(z_1) \oplus (1-\lambda)
         T(z_2)\\
        \subseteq &\lambda\underbrace{(\{z_1\}\oplus T(z_1))}_{\subseteq S}\oplus
        (1-\lambda)\underbrace{(\{z_2\}\oplus T(z_2))}_{\subseteq S}\\
        \subseteq& Z
        \end{aligned}\]
%      \end{equation}
      where the last inclusion follows from the convexity of $\mathcal S$.
    \end{proof}

    In the given setup we consider a point-to-set map defined by
    \begin{equation}\label{eq:definition:disturbance:set}
      \mathcal V(x) = \{v:\,G v \leq H(x)\}
    \end{equation}
    where $H$ is elementwise convex in $x$, so that 
    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for 
    $\lambda\in[0,1]$.  For such sets we have the following result.
    \begin{thm}\label{thm:convex:parametric:set}
      $\mathcal V (x)$ defined in~\eqref{eq:definition:disturbance:set} is parametrically convex.
    \end{thm}
    \begin{proof}
      To show that $\mathcal V(\lambda x_1 + (1-\lambda)x_2)\subseteq 
      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ we note that
        \begin{align*}
        \mathcal V&(\lambda x_1 + (1-\lambda)x_2)\\
        =& \{v:\; G v \leq H(\lambda x_1 + (1-\lambda)x_2)\}\\
        \subseteq& \{v:\;Gv\leq\lambda H(x_1)+(1-\lambda) H(x_2)\}\\
        =&\{v:\;Gv\leq\lambda H(x_1)\}\oplus\{v
        :\;Gv\leq(1-\lambda)H(x_2)\}\\
        =&\lambda\mathcal V(x_1)\oplus(1-\lambda)\mathcal V(x_2).
        \end{align*}
\vskip-1.5\baselineskip
    \end{proof} 
\def\genmat{\Xi} \def\genvec{\xi}Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
and~\ref{thm:convex:parametric:set} imply that the difference of a convex set and 
$\mathcal V(x)$ is a convex set.
Furthermore, we will see that if $\mathcal X$ is polyhedral and $\mathcal 
V(x)$ is as defined in~\eqref{eq:PWA:distrubance:set}, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
again a polytopic set. This will become more clear in the next section when we describe 
the computation of the mRPI set~\eqref{eq:definition:mrpi:set:state:dependent}.

\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}

@@

@@

@@

\section{Example}
Let $\mathcal X\subset\mathbb R^n$ be open, $f : \mathcal X \rightarrow\mathbb R^m$ continuously differentiable, 
	f(x+th) = f(x) + \left(\int_0^1 \frac{\partial f}{\partial x}(x+th)dt\right)\cdot h.

@@

\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}
\section{Example}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,MyLib}

>>>>

\usepackage{graphics}
\usepackage{epsfig}
% \usepackage{mathptmx}
% \usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{lpic}
% \usepackage{blkarray}
\usepackage{mathrsfs}

@@

\begin{document}
  \title{Advances in Robust Positive Invariant Set Computation}

@@

\section{Introduction}
Ever since the introduction of disturbance invariant sets in~\cite{Glover:1971}, the analytic
properties of these sets have been fairly well studied, see~\cite{blanchini:2007}. Here by disturbance
invariant sets we mean set $\mathscr X$ containing initial conditions for the perturbed linear system
\begin{equation}\label{eq:system:equation}
	x^+ = \Psi x + v,
\end{equation}
where $\Psi$ is Hurwitz, $x,x^+\in\mathbb R^n$ the state and the successor state, and where 
$v\in\mathscr V$ denotes the perturbation, such that the successor state is contained in the 
disturbance invariant $x^+\in\mathscr X$ set for all possible realisations of the 
perturbation $v\in\mathscr V$. That is summarised in the implicit definition
\begin{equation}\label{eq:definition:mrpi:set:state:dependent}
	\mathscr X = \{x:\Psi x + v\in\mathscr X\; \forall v\in\mathscr V\}.
\end{equation}
These sets are known as robust positive invariant (RPI) sets, for obvious reasons we are interested 
the largest such set, i.e. the set containing all other RPI sets $\mathscr X\subseteq\mathcal X^\infty$,
this set is called the maximal robust positive invariant (mRPI) set. Even though analytical properties
of these sets were derived early after their introduction, it took more than two decades until algorithms
were introduced to numerically compute mRPI sets~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. Earlier algorithms
did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, or 
did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
%
In the afore mentioned algorithms the perturbation was considered to belong to a fixed compact set, in this paper
we consider sets that vary with parameters. First we consider the set of disturbances to be state dependent, i.e.
\begin{equation}\label{eq:PWA:distrubance:set}
	\mathcal V(x) = \left\{v: Gv\leq\max\{{\bf{1}},H^x x\}\right\},
\end{equation}
where the maximum is understood to be element-wise. This means that in the first part of the paper
we will discuss the computation of $\mathcal X^\infty$ for the case where $\mathscr V=\mathcal V(x)$.
The case where the disturbance depends on the state has been studied analytically before but not 
extensively, see~\cite{Kuntsevich:1995}.

The second case we consider is the case of a scaled set of disturbance, i.e.
\begin{equation}
  \mathcal V(\theta) = \{v:Gv\leq(1+\theta){\bf{1}}\},
\end{equation}
with $\theta>-1$. To distinguish the resulting sets from regular mRPI sets we use $\mathcal Z^\infty$
to emphasise that $\mathcal Z^\infty$ itself is not an mRPI set, however by fixing $\theta=\hat\theta$ the
set $\mathcal Z^\infty\vert_{\hat\theta}$ is an mRPI set. To our best knowledge, this setup has not been 
presented in the literature.

The remainder of this paper is structured: In section~\ref{sec:parametrically:convex:set:operations} we
introduce the notion of \emph{parametric convexity} and of its general implications, this is necessary 
for the convexity of the mRPI set. The algorithm to compute the mRPI set for state dependent disturbance
constraints is presented in section~\ref{sec:state:dep:mrpi}, we also prove its finite determinability.
In section~\ref{sec:first:example} we demonstrate the algorithm using a numerical exemplary system, a
levitating ball setup. The case of scaled disturbance constraints is discussed in section~\ref{sec:mRPI:parametrised}
where the algorithm for the parametrised mRPI set as well as the proof for its finite determinability
are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised mRPI sets using
again the levitating ball example and illustrating some of possible robustness analyses of the parametrised
mRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.
%
%
%
\section{Parametrically convex set operations}\label{sec:parametrically:convex:set:operations}
In this section we discuss sets that depend on a state-like parameter (so called point-to-set maps, 
see~\cite{Hogan:1973}), and extend the existing set algebra~\cite{blanchini:2007} to 
accommodate such sets. We present the general case first, then derive the computation of
the case with piece-wise affine sets.
%
%
    \begin{defn}[Parametric Convexity]\label{def:parametric:convexity}
      Let $X\subseteq\mathbb R^n$ and $Y\subseteq\mathbb R^m$ and $T:X\rightarrow Y$, $X\ni s\mapsto T(s)\subset Y$ be a 
      continuous point-to-set map. The map $T$ is called \emph{parametrically convex} if it satisfies
      \begin{equation}\label{eq:pconvexdef}
        T(\lambda s_1 + (1-\lambda)s_2)\subseteq\lambda T(s_1) \oplus (1-\lambda) T(s_2)
      for all $s_1,s_2\in X$ and $\lambda\in[0,1]$.
    \end{defn}
%
In (\ref{eq:pconvexdef}), $\oplus$ denotes the Minkowski set addition
        \mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}.
%
    In the following we will need to be able to compute differences of sets
    analogous to the Pontryagin difference in~\cite{Kolmanovsky:1998} but using parametrised 
    sets, this is defined as follows:
%
    \begin{defn}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
Let $S\subseteq X$ and let $T:X\to X$ be a continuous point-to-set map,
then the \emph{parametric Pontryagin difference} $S\ominus T(S)$ is 
        S\ominus T(S) = \left\{x\in X: \{x\} \oplus T(x)\subseteq S\right\},
      where $T(S)$ denotes the image of $S$ under the map $T$.
    \end{defn}
%

@@

%
    \begin{thm}\label{thm:convexity:of:pontryagin:difference}
      Let $S\subseteq X$ be a convex set and let $T:X\rightarrow X$ be a parametrically convex point-to-set
      map, then $S\ominus T(S)$ is convex. 
%
      Define $ Z =  S\ominus T( S)$ and let $z_1,z_2\in Z$, then
      by definition of the parametric Pontryagin difference, we have
        \{z_i\} \oplus T(z_i) \subseteq S,\; i=1,2.
      To see that $ Z$ is convex we show that line segments between
      all possible $z_1$ and $z_2$ are subsets of $ Z$, i.e.~for all $\lambda \in [0,1]$,
      \[\begin{aligned}
        \{ \lambda z_1 + (1-&\lambda)z_2
        \}\oplus T\left( \lambda z_1 + (1-\lambda)z_2\right)\\
        \subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
        \right\}\oplus \lambda T(z_1) \oplus (1-\lambda)
         T(z_2)\\
        \subseteq &\lambda\underbrace{(\{z_1\}\oplus T(z_1))}_{\subseteq S}\oplus
        (1-\lambda)\underbrace{(\{z_2\}\oplus T(z_2))}_{\subseteq S}\\
        \subseteq& Z
        \end{aligned}\]
      where the last inclusion follows from the convexity of $\mathcal S$.
%
%
    In the given setup we consider a point-to-set map defined by
    \begin{equation}\label{eq:definition:disturbance:set}
      \mathcal V(x) = \{v:\,G v \leq H(x)\}
    where $H$ is elementwise convex in $x$, so that 
    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for 
    $\lambda\in[0,1]$.  For such sets we have the following result.
    \begin{thm}\label{thm:convex:parametric:set}
      $\mathcal V (x)$ defined in~\eqref{eq:definition:disturbance:set} is parametrically convex.
%
      To show that $\mathcal V(\lambda x_1 + (1-\lambda)x_2)\subseteq 
      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ we note that
        \begin{align*}
        \mathcal V&(\lambda x_1 + (1-\lambda)x_2)\\
        =& \{v:\; G v \leq H(\lambda x_1 + (1-\lambda)x_2)\}\\
        \subseteq& \{v:\;Gv\leq\lambda H(x_1)+(1-\lambda) H(x_2)\}\\
        =&\{v:\;Gv\leq\lambda H(x_1)\}\oplus\{v
        :\;Gv\leq(1-\lambda)H(x_2)\}\\
        =&\lambda\mathcal V(x_1)\oplus(1-\lambda)\mathcal V(x_2).
        \end{align*}
\vskip-1.5\baselineskip
%
%
\def\genmat{\Xi} \def\genvec{\xi}Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
and~\ref{thm:convex:parametric:set} imply that the difference of a convex set and 
$\mathcal V(x)$ is a convex set.
Furthermore, we will see that if $\mathcal X$ is polyhedral and $\mathcal 
V(x)$ is as defined in~\eqref{eq:PWA:distrubance:set}, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
again a polytopic set. This will become more clear in the next section when we describe 
the computation of the mRPI set~\eqref{eq:definition:mrpi:set:state:dependent}.
%
%
%
%
\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:mrpi}

@@

%

@@

%
\begin{thm}\label{thm:finite:mRPI:set:state:dependable}

@@

%
%
%
\section{Example}\label{sec:first:example}
%
%

@@

%
%
%
%
%
%
%
\begin{thm}\label{thm:mean:value:theorem}
Let $\mathcal X\subset\mathbb R^n$ be open, $g : \mathcal X \rightarrow\mathbb R^m$ continuously differentiable, 
	g(x+h) = g(x) + \left(\int_0^1 \frac{\partial g}{\partial x}(x+th)dt\right)\cdot h.
%
%
Using the mean value theorem~\ref{thm:mean:value:theorem}
and the linearisation for $\Delta x = \hat x + \tilde x$ and $\Delta u = \hat u + \tilde u$ we
get the successor state:
%
	\Delta x^+ = \underbrace{\tilde f(\hat x, \hat u)}_{\hat x} + \int_0^1\frac{\partial\tilde 
	f}{\partial x}(\hat x + t\tilde x
	,\hat u + t\tilde u)dt\cdot \tilde x +\\
	 \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x
	,\hat u + t\tilde u)dt\cdot \tilde u + A \tilde x + B \tilde u - A \tilde x - B\tilde u\\
	\Leftrightarrow \tilde x^+ = A\tilde x + B \tilde x +\left(
	\int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u + t\tilde u)dt - A
	\right)\tilde x + \\ \left(
	\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u + t\tilde u)dt - B
	\right)\tilde u
	\end{split}
%
This implies that for any linearised state $\tilde x$ we obtain the expression
$\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u$, however the computation
of $H^x$ and $H^u$ requires solving a nonlinear integral. Assume that inside given compact system
constraints $\mathcal X$ and $\mathcal U$ we had extremal values of $H^x$ and $H^u$, i.e.
$H^x\tilde x+H^u\tilde u\in\conv_k\{H^x_k\tilde x + H^u_k\tilde u\}$ for all $(\tilde x,\tilde u)\in\mathcal X\times \mathcal U$.
Clearly, we can then introduce the element wise bound disturbance 
%
\begin{equation}\label{eq:definition:element:wise:constraints:on:nonlinearities}
\mathcal V(x,u)=\left\{v:\min_k\{
H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge\right. \\ \left.v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}\, i =1,\dots,n\right\}.
\end{split}
%
With this set we can
guarantee that $\tilde x^+ = A\tilde x + B\tilde u + v$ accounts for all nonlinearities within $\mathcal X
\times\mathcal U$ if we constraint $v\in\mathcal V(\tilde x,\tilde u)$. For general nonlinear systems
finding the extremal values of $(H^x,H^u)$ can not be done easily, so for the example of the 
levitating ball we use the parameters: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
\abs{\hat x_1-x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{\hat u-u}\leq10mA\}$.
Using 25 samples of $(H^x,H^u)$ we obtain the invariant set shown in figure~\ref{fig:mrpi:set:levitating:ball},
which is less conservative than using fixed bounds on the nonlinearities as we will see in the next example.
%
%
\begin{lpic}{invariantSetStateDependant(.65,)}
{\tiny
\lbl[r]{9,94; $0.1$}
\lbl[r]{9,86; $0.08$}
\lbl[r]{9,78; $0.06$}
\lbl[r]{9,70; $0.04$}
\lbl[r]{9,63; $0.02$}
\lbl[r]{9,55; $0$}
\lbl[r]{9,47; $-0.02$}
\lbl[r]{9,39; $-0.04$}
\lbl[r]{9,32; $-0.06$}
\lbl[r]{9,24; $-0.08$}
\lbl[r]{9,16; $-0.1$}
\lbl[t]{11,9; $-6$}
\lbl[t]{30,9; $-4$}
\lbl[t]{48,9; $-2$}
\lbl[t]{67.5,9; $0$}
\lbl[t]{86,9; $2$}
\lbl[t]{104,9; $4$}
\lbl[t]{123,9; $6$}
\lbl{120,3; $\times10^{-3}$}
}
{\small
\lbl{68,3; $\tilde x_1$}
\lbl{0,55,90; $\tilde x_2$}
}
\caption{The maximal robust positive invariant set for the levitating ball system.}
\label{fig:mrpi:set:levitating:ball}
%
%
%
%
%
\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}\label{sec:mRPI:parametrised}
%
%
In this section we describe the computation of the mRPI set for~\eqref{eq:system:equation}
but using a disturbance set that is parametrised for scaling, i.e. $\mathcal V(\theta) = \{v: Gv\leq(1+\theta){\bf{1}}\} 
= (1+\theta)\mathcal V(0)$, for $\theta>-1$. We will be able to combine the uniform scaling of 
the disturbance set $\mathcal V(\theta)$ with non-uniform scaling of the input constraint set
$\mathcal U({\bf{\alpha}}) = \{u: Fu\leq\left(I+\text{diag}(\alpha_1,\dots,\alpha_p)\right){\bf{1}}\}$, 
this can be used to study closed loop systems subject to a given feedback controller.
%
\begin{rem}
The set $\mathcal V(\theta)$ is nonempty and contains the origin for all $\theta>-1$ and hence the 
maximum
%
0<\begin{array}{rl}
\max & c^T v\\
\text{s.t.}& Gv \leq (1+\theta){\bf{1}}\\
&\theta>-1
\end{array}
%
is positive for any nonzero $c$.
\end{rem}
%
In the following we describe an algorithm to compute the mRPI set $\mathcal Z^\infty$ contained in 
$\mathcal Z = \{(x,\theta):\mathcal F_i x+\mathcal G_i\theta \leq 1,\forall\, i\leq m\}$.
As in the state dependent case we iteratively introduce constraints \emph{cutting off} points
for which the successor state can lie outside the previous set, i.e. starting from $Z_0 = \mathcal Z$
we determine the first iterate by enforcing all individual constraints onto all possible successor states:
$Z_1=Z_0\cap D_0$ where $D_0$ is defined by
%
\begin{equation}\small
	D_0 =& \{\mathcal F_i(\Psi x+v) + \mathcal G_i\theta \leq 1 \forall\, v\in\mathcal V(\theta), i\leq m\}\\
	=&\left\{\mathcal F_i\Psi x + \begin{array}{rl}\max& F_i v \\ \text{s.t.}& Gv \leq 
	(1+\theta){\bf{1}} \\ &\theta>-1\end{array}
	 + \mathcal G_i \theta \leq 1 \forall\, i\leq m\right\}\\
	=&\left\{\mathcal F_i\Psi x + (1+\theta)\underbrace{\begin{array}{rl}\max& F_i v \\ 
	\text{s.t.}& Gv \leq {\bf{1}}\end{array}}_{v_{0,i}^\ast}
	 + \mathcal G_i \theta \leq 1 \forall\, i\leq m\right\}\\
	=&\{\mathcal F_i\Psi x + (\mathcal G_i + v_{0,i}^\ast)\theta \leq 1 - v_{0,1}^\ast \forall i\leq m
	\}
%
Using the same principle we define $Z_{k+1}=Z_k\cap D_k$ with $D_k$ given by
%
\begin{equation}\label{eq:parametrised:Dk}\small
	D_k = \{\mathcal F_i\Psi^{k+1}x+ \left(\mathcal G_i +\sum_{0\leq l\leq k} v_{l,i}^\ast\right)\theta \leq 1 
	- \sum_{0\leq l\leq k} v_{l,i}^\ast\, i\leq m\}
%
where we use 
%
\begin{equation}\label{eq:definition:v:ast}
v_{l,i}^\ast = \begin{array}{rl}\max & \mathcal F_i \Psi^{l} v \\ \text{s.t.}& Gv\leq{\bf{1}}
\end{array}
%
Notice that~\eqref{eq:definition:v:ast} can be represented in various ways:
%
\begin{array}{rl}
\max&\mathcal F_i \Psi^l v \\ \text{s.t.}&v\in\bar{\mathcal{V}}
\end{array} = 
\begin{array}{rl}
\max&\mathcal F_i \tilde  v \\ \text{s.t.}&\Psi^{-l} \tilde v\in\bar{\mathcal{V}}
\end{array} = 
\begin{array}{rl}
\max&\mathcal F_i v \\ \text{s.t.}& \tilde v\in\Psi^l\bar{\mathcal{V}}
\end{array}
%
$\bar{\mathcal{V}}=\mathcal V(0)$ for notational convenience. So that for any fixed $\hat\theta>-1$
we have the closed form description
%
\begin{equation}\label{eq:closed:form:parametrised:iterates}
	Z_{k+1}\vert_{\hat\theta} &= Z_{k}\vert_{\hat\theta}\cap\left(
	\Psi^{-1}Z_k\vert_{\hat\theta}\ominus\Psi^{k-1}\mathcal V(\hat\theta)\right)\\
	&=\bigcap_{l\leq k}\left(\Psi^{-l}\mathcal Z\vert_{\hat\theta}\underset{i\leq l-1}{\bigominus} 
	\Psi^i \mathcal V(\hat\theta)
	\right).
\end{split}
%
The iteration terminates when $Z_k\subseteq Z_{k+1}$. Like in section~\ref{sec:state:dep:mrpi}
we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band, i.e. that 
the set $\{x:\mathcal Fx \leq {\bf{1}}-\mathcal G\hat\theta\}=\mathcal Z\vert_{\hat\theta}\subseteq
\mathcal B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma x\leq {\bf{1}}\}$ for all $\hat\theta>-1$. We have the
%
Let the system constraints be contained in a band $\mathcal Z\vert_{\hat\theta}\subseteq\mathcal 
B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma x\leq {\bf{1}}\}$ for any fixed $\hat\theta$, let the
pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(0)$ be bounded, then $Z_N\subseteq Z_{N+1}$
for a finite $N$. Hence the mRPI set $\mathcal Z^\infty = Z_N$ is a finite polyhedron.
%
The argumentation in this completely analogue to the one in Lemma~\ref{thm:finite:mRPI:set:state:dependable}.
First we argue that for each fixed $\hat\theta$ the set $Z_k\vert_{\hat\theta}$ becomes compact using the same
observability argument as in Lemma~\ref{thm:finite:mRPI:set:state:dependable}.
We then use the representation~\eqref{eq:closed:form:parametrised:iterates} to argue that $D_k$ as
in~\eqref{eq:parametrised:Dk} grows exponentially and therefore contains any compact set after a finite number
of iterations. The fact that $\theta$ was fixed to $\hat\theta$ does not change anything since
our argument is constructed for a fixed matrix $\Gamma$ where the rows had to be scaled by 
$\frac{1}{1-\mathcal G_i\hat\theta}$ and we could rescale them to accommodate any other choice of $\hat\theta>-1$.
We now have a way to scale the the disturbance set uniformly, as mentioned earlier we can extend the algorithm
to accommodate non uniformly parametrised input constraints to accommodate more degrees of freedom for 
system analysis by simply using $\mathcal Z = \{(x,\theta,\alpha): \mathcal F x + \mathcal G\theta + 
\mathcal H \alpha \leq {\bf{1}}\}$. This does not affect the algorithm since at each step of the iteration 
the elements of $\mathcal H$ remain unchanged. In the next section we will illustrate the algorithm.
%
%
%
%
%
%
\section{Example}\label{sec:second:example}
%
%
In this section we compute the mRPI set for the levitating ball exemplary system presented in 
section~\ref{sec:first:example} as well as for a direct torque fed pendulum to illustrate both
the effectiveness of the afore presented algorithm for state dependent disturbances as well as
the system analysis tool that is the parametrised mRPI set. First we present the parametrised mRPI
set for the levitating ball, notice that in order to obtain comparable results we need to get fixed bounds
on the effect of nonlinearities on each state, i.e. a constant version 
of~\eqref{eq:definition:element:wise:constraints:on:nonlinearities}. Using the same constraint set 
$\mathcal X \times \mathcal U$ to determine the maximal and minimal values for nonlinear effects
we obtain a constant set which is non symmetric around the origin due to nonlinearity. We also introduce
a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$. For this setup we obtain the mRPI
set $\mathcal Z^\infty=\{(x,\theta,\alpha): \Lambda_i^x x + \Lambda_i^\theta \theta + \Lambda_i^\alpha \alpha\leq
\lambda_i\,\forall i\leq m_\infty\}$. Notice that since $\alpha$ was introduced as a scaling parameter
for $\mathcal U(\alpha)=\{u: Fu\leq (1+\alpha){\bf{1}}\}$ all entries in $\mathcal H$ are non positive and
remain unchanged throughout the computation of $\mathcal Z^\infty$ so that $\Lambda^\alpha$ has only non
positive entries, i.e. increasing $\alpha$ will enlarge the parametrised mRPI set $\mathcal Z^\infty\vert_{\alpha_1}
\subseteq\mathcal Z^\infty\vert_{\alpha_2}$ for $\alpha_1\leq\alpha_2$.

First we want to compare the mRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
constraints with the parametrised one $\mathcal Z^\infty$. To do this we compute the scaling parameter 
$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(0,\alpha_{\min})}$.
We can do this by solving $m_\infty$ linear programs
%
%
\[
	\gamma_i^\ast = \left\{\begin{split}
	\max& \;\Lambda_i^x x\\
	\text{s.t.}& \;x\in\mathcal X^\infty
	\end{split}
	\right.
\]
%
%
The minimal value for $\alpha_{\min}$ is then given by the maximal $\alpha$ satisfying $\gamma_i^\ast + 
\Lambda_i^\theta\cdot 0 + \Lambda_i^\alpha \alpha \leq \lambda_i$. Solving this we obtain the 
minimal value $\alpha_{\min} = 1.7555$ and the mRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:mRPIs}.
Caution is advised when interpreting $\alpha>0$, since the system is nonlinear extrapolations bare very
little insight, the only information we can safely extract is that the current set of inputs $\mathcal U(0)=\mathcal U$ 
is not large enough to cope with the perturbation set containing given by upper bounds of the nonlinear effects.
%
%
\begin{figure}
\begin{lpic}{minimalAlphaForConstantDisturbance(.65,)}
{\tiny
\lbl[r]{7,87;$1.5$}
\lbl[r]{7,69;$1$}
\lbl[r]{7,51;$0.5$}
\lbl[r]{7,34;$0$}
\lbl[r]{7,16;$-0.5$}
\lbl[t]{15,2;$-0.06$}
\lbl[t]{27,2;$-0.05$}
\lbl[t]{39,2;$-0.04$}
\lbl[t]{51,2;$-0.03$}
\lbl[t]{63,2;$-0.02$}
\lbl[t]{75,2;$-0.01$}
\lbl[t]{89,2;$0$}
\lbl[t]{100,2;$0.01$}
\lbl[t]{113,2;$0.02$}
}
{\footnotesize
\lbl[r]{5,45,90;$\tilde x_2$}
\lbl[t]{121,3;$\tilde x_1$}
}
\lbl[l]{93,32;$\longleftarrow\mathcal X^\infty$}
\lbl[r]{68,43;$\mathcal Z^\infty\vert_{(\alpha_{\min},0)}\longrightarrow$}
\end{lpic}
\caption{Minimal scaling for mRPI set computed for constant disturbance which contains
 mRPI set for piecewise affine disturbances is $\alpha=1.7555$. Note that since the nonlinearities of the system
 dynamics are not symmetrical around the equilibrium the mRPI set with fixed constraints on the perturbation
 is non-symmetric.}
 \label{fig:minimal:scaling:comparison:mRPIs}
\end{figure}

In the second example we compute the parametrised mRPI set for the system
$$
x^+ = \underbrace{\left(\begin{array}{cc}1 & 2 \\ 0 & 1\end{array}\right)}_Ax + 
\underbrace{\left(\begin{array}{cc} 1 & 1 \\ 1 & -1\end{array}\right)}_B u + 
\underbrace{\left(\begin{array}{cc} 1 & 2 \\ 2 & 1 \end{array}\right)}_D w
$$
We use the constraint sets $\mathcal U(\alpha) = \{u: Fu\leq(I+\text{diag}(\alpha)){\bf{1}} \wedge
-Fu\leq (I+\text{diag}(\alpha)){\bf{1}}\}$ and $\mathcal V(\theta) = D\mathcal W(\theta)$ where $\mathcal W(\theta) = \{w:
\abs{w_1}\leq 0.1(1+\theta)\wedge \abs{w_2}\leq 0.15(1+\theta)\}$. The constraint matrix $F$ is given by
$$
	F = \left(\begin{array}{cc} 2 & 2 \\ 4 & 0 \\ 2 & -2 \end{array}\right).
$$
We can now analyse the effect of changing individual constraints on the input by changing $\alpha$ as well as the
effect of perturbations. To initialise the iteration we use
$\mathcal Z(x,\theta,\alpha) = \left\{(x,\theta,\alpha): Kx\in\mathcal U(\alpha)\wedge K_w x\in\mathcal W
(\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, with $K$ and $K_w$ being the solution to the semidefinite program
$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$, i.e. $K_w = (\gamma^2-D^TPD)D^TP(A+BK)$.
We use $Q = \text{diag}(2,1)$ and $R = I$. Using these numerical values we determine the mRPI set 
$\mathcal Z^\infty$ after 22 iterations, it has 61 facets. Notice that in addition to the sign of 
the sensitivity of the mRPI set on $\alpha$ we know that since we introduced each facet of $\mathcal Z$
to depend only on one $\alpha_i$, since the algorithm does not change the elements corresponding to $\alpha$
and due to orthogonality two facets depending on different elements of $\alpha$ can not be reduced to 
one facet depending on both. I.e. $\Lambda^\alpha$ has no more than one entry per row. We can therefore 
compute which $\alpha_i$ will change the mRPI set the most. This can be done by element wise calculating
$$
	\max_i  \frac{-\Lambda_i^\alpha}{\norm{\Lambda_i^x}_2}.
$$
In our example the greatest sensitivity corresponds to $\alpha_3$ with a numerical value of $2.6458\times 10^9$, 
i.e. the third input constraint.
